Joe Biden won popular votes in 2024 US Presidential Election

### 2024-03-09 outputs/paper.qmd
improve graphs

data2 <- inner_join(data1, vote_for_biden, by = "statename") |> filter(vote_biden == '1')

```

@@

@@

>>>>

data2 <- inner_join(data1, vote_for_biden, by = "statename") |> filter(vote_biden == '1')
```

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-coefficients_model2
#| fig-cap: Estimates of Coefficients in the Model (Balanced)
coefficients_20 |> 
  ggplot(aes(x = estimate, y = term)) + 
  geom_point() +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), color = "orange3", position = position_dodge(width = 0.2)) +
  labs(x = "Estimates", y = "Coefficients") +
  theme_bw() + 
  theme(axis.text.y = element_text(size = 4.5))
```

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-sample_and_population_20
#| fig-cap: Proportion of Voters in Each State Voting for Biden (Balanced)
data4 |>
  ggplot(aes(x = statename, y = biden_predict_20 * 100)) +
  geom_point(aes(color = "Biden Prediction"), size = 2) + 
  geom_line(aes(group = 1), linetype = "solid", size = 0.8) +
  geom_ribbon(aes(group = 1, ymin = biden_lower_20 * 100, ymax = biden_upper_20 * 100), alpha = 0.2, fill = "orange2") +
  geom_line(aes(x = statename, y = prop * 100, group = 2), 
            linetype = "dashed", color = "red2", size = 0.8) +
  geom_point(data = data4, aes(x = statename, y = prop * 100, color = "Population"), size = 2) +
  geom_hline(aes(yintercept = 40), alpha = 0.5, linetype = "dotted", color = "gray") +
  geom_hline(aes(yintercept = 60), alpha = 0.5, linetype = "dotted", color = "gray") +
  geom_hline(aes(yintercept = 80), alpha = 0.5, linetype = "dotted", color = "gray") +
  geom_hline(aes(yintercept = 50), alpha = 0.6, color = "orange3") +
  scale_color_manual(name = "Data", values = c("Biden Prediction" = "black", "Population" = "red2"), labels = c("Population Prediction", "Survey Sample (Balanced)")) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 55, size = 6, hjust = 1, vjust = 1),
        legend.position = "bottom",
        legend.title = element_text(size = 10),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  labs(x = "State", y = "Voting Percentage for Biden (Balanced)")
```
